    %-------------------------
% Resume in Latex
% Author
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Hemant Shankar} % Your Name
\newcommand{\phone}{9354535461 | \href{https://hemant-shankar-portfolio.onrender.com/}{\textcolor{blue}{Portfolio}}} % Your Phone Number
\newcommand{\emaila}{hemantshankar9595@gmail.com} %Email 1

\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name}\\
  \href{mailto:hemantshankar9595@gmail.com}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} & \href{https://github.com/HemantShankar}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {\textcolor{blue}{Github}}} \\  
  {\raisebox{0.0\height}{\footnotesize \faPhone}\ +91-\phone} & \href{https://www.linkedin.com/in/hemant-shankar}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {\textcolor{blue}{LinkedIn}}}
\end{tabularx}
}
\vspace{-4mm}
%-----------Career Objective-----------
\section{\textbf{Professional Summary}}
\item A recent graduate in Integrated M.S in Mathematics and Computing from NIT Agartala, with a CGPA of 8.47. Interested in data science, machine learning, and research-driven problem solving. Cleared GATE DSAI for two consecutive years. Actively seeking opportunities to apply analytical and technical skills in real-world projects. Skills: Python, MATLAB, R, SQL, TensorFlow.
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      { Integrated Masters of Science(MS) in Mathematics and Computing}{CGPA: \textbf{8.47}}
      {\textbf{National Institute of Technology Agartala}}{December 2020 - May 2025}
      \vspace{0.3cm}
      \small Data Structures \& Algorithms, Financial Mathematics, Artificial Intelligence, Linear and
Abstract Algebra, Decision Theory and
Computational Statistics, Machine Learning, 
Probability and Statistics
  \resumeSubHeadingListEnd
\vspace{-8.0mm}
%

%-----------EXPERIENCE-----------------
\section{\textbf{Professional Experience}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Machine Learning Intern}{Onsite}
      {Aryabhatta Research Institute of Observational Sciences(ARIES), Nainital}{May 2023 - July 2023}
      % \vspace{-2.0mm}
      \resumeItemListStart
    \item Applied and compared \textbf{5+} machine learning models for \textbf{regression and clustering} on real-world astronomical datasets, improving research insights and accuracy by over \textbf{25{\%}}.
    \item Developed a modular preprocessing pipeline, reducing .Mcs file processing time by \textbf{95{\%}}.
    \item Built a custom clustering model for the HEPL dataset that enabled the discovery of hidden patterns, assisting researchers in hypothesis generation and interpretation.
    \resumeItemListEnd
\vspace{-1mm}
    \resumeSubheading
      {Freelance Prompt Training Associate}{Remote}
      {Outlier AI}{Jan 2024 - October 2024}
      % \vspace{-2.0mm}
      \resumeItemListStart
    \item Curated and structured over \textbf{15,000+} input-output prompt pairs to enhance the performance of AI models on mathematical and computational tasks.


    \item Improved prompt clarity and consistency, resulting in a \textbf{15–20{\%}} boost in model response accuracy based on internal evaluation metrics.
    \item Maintained version control and documentation for multiple prompt datasets, enabling updates and reproducibility.
    \resumeItemListEnd
    \vspace{-3.5mm}
%-----------PROJECTS-----------------
\section{\textbf{Personal Projects}}
\resumeSubHeadingListStart
    \resumeProject
      {Weather Wizard | \href{https://github.com/HemantShankar/Weather_Wizard}{\textcolor{blue}{Notebook Link}}} %Project Name
      {A Multilevel LSTM model for weather prediction} %Project Name, Location Name
      {March 2025 – April 2025} %Event Dates

      \resumeItemListStart
        \item Developed a time-series forecasting model using \textbf{Multilevel LSTM} and \textbf{TensorFlow}, achieving over \textbf{97{\%}} prediction accuracy on structured computational datasets.




\item Engineered a preprocessing pipeline to transform and scale \textbf{1,00,000+} data points, improving model training stability and reducing input variance by \textbf{30{\%}}.
\item Created visualization tools using Matplotlib to analyze predictions across 50+ time steps, enabling better interpretability and performance tracking.
\item \textbf{Tech Stack}: Python, Tensorflow, Scikit-learn, Pandas, Time Series, Matplotlib, Plotly, Git
    \resumeItemListEnd
    % \vspace{-2mm}
    
    \resumeProject
      {Fly India | \href{https://github.com/HemantShankar/Indian-Flight-Fare-Analysis}{\textcolor{blue}{Notebook Link}}} %Project Name
      {Dashboard of Indian Flight Analysis } %Project Name, Location Name
      {April 2024 – May 2024} %Event Dates

      \resumeItemListStart
        \item Conducted EDA on flight data from six metro cities to uncover fare patterns and airline trends.

\item Built a flight comparison tool and interactive Power BI dashboard to help users make informed travel decisions.

\item Utilized Python libraries like NumPy, Pandas, Seaborn, and Matplotlib for analysis and visualization.
\item \textbf{Technologies}: Python, Jupyter Notebook, PowerBI, and Git.
    \resumeItemListEnd
    % \vspace{-2mm}

    \resumeProject
      {Netflix Analyzer | \href{https://github.com/HemantShankar/Netflix_Analysis}{\textcolor{blue}{Repo Link}}} %Project Name
      {An analysis on Netflix's Movies and Web Series} %Project Name, Location Name
      {Sep 2023 - Sep 2023} %Event Dates

      \resumeItemListStart
        \item Analyzed over \textbf{8,000} Netflix titles using SQL queries to reveal genre distribution, release trends, and content gaps.
    \item Created analytical dashboards for platform content strategy insights.
    \item Provided insights into the type and quality of Netflix content.
    \item \textbf{Tech Stack}: MySQL, Git.
    \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-7.5mm}



    
  %   \resumeSubheading
  %     {Palo Alto Cybersecurity Virtual Internship}{Online}
  %     {AICTE-Eduskills}{Dec 2022 - Feb 2023}
  %     \vspace{-2.0mm}
  %     \resumeItemListStart
  %   \item {Learned the fundamentals of Security Operations Center (SOC).}
  %   \item {Learned basics of Network \& Cloud Security.}
  %   \resumeItemListEnd
    
  %   \vspace{-3.0mm}
      
  % \resumeSubHeadingListEnd
% \vspace{-5.5mm}







%-----------Technical skills-----------------
\section{\textbf{Technical Skills and Interests}}
\begin{itemize}[leftmargin=0.05in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, SQL, MATLAB } \\
     \textbf{Framework \& Libraries}{: PyTorch, Scikit-learn, LSTM, CNN, RNN, NumPy, Pandas, Matplotlib, Seaborn} \\
     \textbf{Data Analysis \& Visualization Tools}{: Jupyter Notebook, Power BI, Tableau, MS Excel, Plotly } \\  
     \textbf{Big Data Technologies}{: Apache Spark, Hadoop, Scala, Hive}, \\
     \textbf{Databases \& Storage}{: MySQL, PostgreSQL, Google BigQuery } \\  
     \textbf{Tools \& Platforms}{: Git, GitHub, VS Code, Google Cloud Platform (GCP), Streamlit} \\
     \textbf{Core Skills}{: Data Science, Statistical Analysis, Data Preparation, EDA, Machine Learning} \\
     \textbf{Deep Learning {\&} AI}{: CNN, RNN, Pytorch, LSTM, Computer Vision, NLP, Image Captioning} \\
    }}
 \end{itemize}
 \vspace{-16pt}
\section{\textbf{Positions of Responsibility}}
\vspace{-2mm}
\resumeSubHeadingListStart
\resumePOR{Head of Operation and Strategies } % Position
    {| Entrepreneurship Cell, NIT Agartala} %Club,Event
    {Aug 2021 - Dec 2023} %Tenure Period \\
    \resumeItemListStart
    % \item We organized Northeastern E-summit \textbf{Carpe Diem 3.0}.
\item Hosted more than 10 \textbf{speaker sessions}, \textbf{workshops}, and \textbf{competitions} to foster a startup ecosystem in Northeast.
    \item Created a significant impact on over \textbf{5,000 people} by providing them an ecosystem for startup growth.
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-7mm}

% -----------------------------------------------------------------
\section{\textbf{Achievement}}
\vspace{-0.4mm}

    \resumeItemListStart
    % \item We organized Northeastern E-summit \textbf{Carpe Diem 3.0}.
\item Cleared \textbf{GATE} DSAI \textbf{for two consecutive years 2024-2025} with \textbf{\href{https://drive.google.com/file/d/1UpbCIcsCu5D63btW4_GaFTny7aUMrL-z/view?usp=sharing}{\textcolor{blue}{GATE Score of 519}}}
    \item \textbf{\href{https://drive.google.com/file/d/1mtsd7VvkWesBoY2TFoTx8x9AE_BZCOOp/view?usp=drivesdk}{\textcolor{blue}{Runner-Up}}} position at IGNITE’21 (Startup Ideation Challenge) among 100+ participants from Northeast India.
    \resumeItemListEnd




% %-----------Achievements-----------------
% \section{\textbf{Achievements}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
    
% \resumePOR{Achievement } % Award
%     {description} % Event
%     {Event dates} %Event Year
% \resumeSubHeadingListEnd
% \vspace{-5mm}


\end{document}
